### 2010-03-05 docs/FAQ/faq.tex
fix options in the initial projection question
add Andy's profiling tip

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = T
\end{verbatim}

>>>>

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = F
\end{verbatim}

\item {\em How can I obtain profiling infomation for my run?}

  The code is already instrumented with timers.  Simply compile with
  {\tt PROF=TRUE} in the {\tt GNUmakefile}, or equvalently do 
  {\tt make PROF=t}
